Palmer Archipelago Penguins Data in the palmerpenguins R Package - An Alternative to Anderson's Irises

### 2021-04-27 penguins.Rmd
fix Palmer Station LTER bibliography entries (#23)

- Adélie penguin data [@lter_structural_2020]: [KNB-LTER Data Package 219.5](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.219.5)
- Gentoo penguin data [@lter_structural_2020-1]: [KNB-LTER Data Package 220.5](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.220.5)
- Chinstrap penguin data [@lter_structural_2020-2]: [KNB-LTER Data Package 221.5](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.221.6)

>>>>

- Adélie penguin data [@lter_structural_2020]: [KNB-LTER Data Package 219.5](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.219.5)
- Gentoo penguin data [@lter_structural_2020-1]: [KNB-LTER Data Package 220.5](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.220.5)
- Chinstrap penguin data [@lter_structural_2020-2]: [KNB-LTER Data Package 221.6](https://portal.edirepository.org/nis/mapbrowse?packageid=knb-lter-pal.221.6)
